---
title: "ABS Data Explore"
author: "Xilin Chen"
date: "3/23/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F,
  comment = NA
)

library(tidyverse)
library(DT)
library(gtsummary)
```

```{r, cache=TRUE}
# ABS data prep -----------------------------------------------------------
abs = data.table::fread(
  "/Volumes/George_Surgeon_Projects/Surgeon Profile data/abs_with_npi.csv",
  colClasses = c("character")
)

selected_abs_gs = abs %>% 
  mutate(residency_graduation_year = ifelse(!is.na(residency_yog),
                                            residency_yog, yot)) %>% 
  select(npi, sex, residency_graduation_year, Gcertyear, Gcompyear, ReCeverPassed,
         PFfirstCE, QEeverPassed, nAttemptsReCert, PFfirstR, us_medschool, gs_specialty_cms, fellowship) %>% 
  mutate(npi = as.character(npi))


abs_gs = selected_abs_gs %>% 
 filter(fellowship == "FALSE", us_medschool != "Foreign_MG" | is.na(us_medschool))

# nrow(abs_gs) #32735

# add medicare gs definition
abs_medicare_gs = abs_gs %>% 
  filter(gs_specialty_cms == "TRUE")

# nrow(abs_medicare_gs) #13259

```

### 1. ABS General Surgery surgeons and Non-foreign med school trained


```{r Input}
radioButtons(
  "define_gs",
  label = "Definition of GS:",
  choices = list(
    "Fellowship from ABS and fellowship council" = 1,
    "Fellowship adding medicare definition" = 2
  ),
  selected = 2
)


```

breakdown of recertification records

```{r}
# define data based on how we define General Surgery surgeons
data_gs <- reactive({
   if(input$define_gs == 1){
    abs_gs 
   } else if (input$define_gs == 2) {
    abs_medicare_gs 
   }
  })
```


```{r output}
renderTable({
  data_gs() %>%
    count(ReCeverPassed, name = "n_surg") %>% 
    mutate(perc = scales::percent(n_surg/sum(n_surg), digits = 1))
})
```



### 2. Define never recertified surgeon group (Define NA)


- at least have 10 years after the initial certification year

breakdown of NA recertification records 

```{r}
# data processing---------------------
# add year after graduation flag and passed CE exam flag
# Only for on record ReCertification surgeon group
data_gs_na = reactive({
  
  # add failed_recert_10yrs flg
  data_gs() %>%
    # filter to NA 
    filter(is.na(ReCeverPassed)) %>%
    mutate(
    Gcertyear = as.numeric(Gcertyear),
    years_after_recertification = 2019 - Gcertyear
  ) %>% 
  mutate(
    # years after initial recertification >10 years,
    # Defined NA that has failed the exam
    failed_recert_10yrs = ifelse(years_after_recertification>10, "failed",
                           "not 10 yrs"),
  )
  
})
```



```{r}
# Include na exclude surgeon table based on year after inital certification
renderTable({
  data_gs_na() %>%
    count(failed_recert_10yrs, name = "n_surg") %>%
    mutate(perc = scales::percent(n_surg/sum(n_surg), digits = 1))

})

# number of surgeons that never passed CE
# This is excluded in our analysis
renderText({
  n_no_pass_in_10yrs = data_gs_na() %>% 
    filter(failed_recert_10yrs == "failed") %>% 
    nrow()

  paste0("The number of surgeons failed to get recertified in 10 years: ",
        n_no_pass_in_10yrs)

})
```


### 3. Grandfather Surgeon effects among never certified surgeons from NA

from ABS paper
> the American Board of Surgery (ABS) introduced time-limited certification in 1976, requiring diplomats certified subsequently to pass a secure, multiple-choice comprehensive recertification examination in surgery every 10 years as demonstration that they remain current with advancements in surgical knowledge.

```{r}
# data process
# get qualified NA surgeons
data_na_qualified_suregons = reactive({
  data_gs_na() %>%
    filter(failed_recert_10yrs == "failed") 
})
```

number of failed to pass (from NA) surgeons in each graduation year 


```{r}
renderPlot({
  data_na_qualified_suregons() %>%
    count(residency_graduation_year) %>% 
    mutate(residency_graduation_year= as.numeric(residency_graduation_year)) %>% 
    ggplot(aes(x= residency_graduation_year, y = n)) +
    geom_point() + 
    theme_classic() +
    theme(axis.text=element_text(size=15),
          axis.title = element_text(size=20))
})

```


```{r}
numericInput("graduation_year", label = "Choose a year to define grandpa surgeons", value = 1976, min = 1900, max = 2019)

```



```{r}
data_na_qualified_suregons_filter_grad_year = reactive({
  data_na_qualified_suregons() %>%
    mutate(
      residency_graduation_year = as.numeric(residency_graduation_year),
      older_surgeon = ifelse(
        residency_graduation_year < input$graduation_year,
        "yes",
        "no"
      )
    )
})

renderTable({  
  data_na_qualified_suregons_filter_grad_year() %>% 
    count(older_surgeon, name = "n_surg") %>% 
    mutate(perc = scales::percent(n_surg/sum(n_surg), digits = 1))
  })
```

### Download Processed dataset

- Exclude no recertification record surgeons who had less than cutoff years after initial certification
- Added 3nd recertification category as "no record, failed" from NA
- added new older_surgeon variable based on graduation year cutoff

```{r}
downloadButton("downloadData", "Download Processed Data")
```

```{r}
processed_data = reactive({
  rbind(
    data_na_qualified_suregons_filter_grad_year() %>% 
      filter(older_surgeon == "no") %>% 
      mutate(ReCeverPassed = "no record, failed"),
    data_gs() %>%
      filter(!is.na(ReCeverPassed)),
    fill = TRUE
  )
})


downloadHandler(
    filename = function() {
      paste0("defined_gs",input$define_gs, "_", "grandpa", input$graduation_year, ".csv")
    },
    content = function(file) {
      write.csv(processed_data(), file, row.names = FALSE)
    }
  )
```




