---
title: "Model Results including fellowship trained"
subtitle: "all procedures, exclude multiple procedures in one admission"
author: "Xilin Chen"
date: "`r Sys.Date()`"
output: 
  html_document:
        toc: yes
        toc_depth: 4
        toc_float:
          toc_collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  fig.align = 'center',
  cache = F
)
library(tidyverse)
library(glmmTMB)
library(marginaleffects)
library(emmeans)
library(kableExtra)
```

```{r}
#load models
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/death_model_bin_3_cert_cat_fellowship.rdata")
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/cmp_model_bin_3_cert_cat_fellowship.rdata")
```

## cohort

```{r}
dt = death_model_bin$frame
```

### Number of Surgeons and case at each certification status

```{r}
dt %>%
  group_by(re_cert_status) %>%
  summarise(
    n_surgon = length(unique(npi)),
    n_case = n()
  ) %>% 
  kable() %>% 
  kable_styling(full_width = F)
```


# model based


## Death

### Model summary

```{r}
summary(death_model_bin)
```

#### Adjusted Prediction at the Mean

The predicted outcome when all the predictors are held at their mean. For categorical predictors, we used all categorical values to make the reference grid but weight the predictions according to their cell frequencies.

```{r}
death_means = emmeans(death_model_bin, "re_cert_status",  type = "response", data = death_model_bin$frame, weights = "cells")

death_means

plot(death_means) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(y = "",
       title = "risk-adjusted rates") +
  medicareAnalytics::theme_cstar()

```

#### Risk ratio

```{r}
pairs(regrid(death_means, transform = "log"), type = "response")
```


## Severe Complication

```{r}
summary(cmp_model_bin)
```

### Adjusted Prediction at the Mean

The predicted outcome when all the predictors are held at their mean. For categorical predictors, we used all categorical values to make the reference grid but weight the predictions according to their cell frequencies.

```{r}
cmp_means = emmeans(cmp_model_bin, "re_cert_status",  type = "response", data = cmp_model_bin$frame, weights = "cells")

cmp_means

plot(cmp_means) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(y = "",
       title = "risk-adjusted rates") +
  medicareAnalytics::theme_cstar()

```

#### Risk ratio

```{r}
pairs(regrid(cmp_means, transform = "log"), type = "response")
```


