---
title: "Compare surgeons in 4 cohort definition"
author: "Xilin Chen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),
  dev = 'png',
  layout = "l-body-outset",
  fig.align = 'center',
  out.width = '75%',
  fig.asp = .75,
  fig.pos = 'H',
  cache = FALSE, 
  cache.rebuild = TRUE
)

source("code/functions/prep_model_ready_dt.R")


library(tidyverse)
library(gtsummary)
library(patchwork)
library(flextable)
library(broom.mixed)

# for table 1
covariates = c(
  # choose one cert status--
  # 're_cert_status',
  're_cert_bin',
  # other--
  'flg_male',
  'age_at_admit',
  'AHRQ_score',
  'race_white',
  'ses',
  'emergent_admit',
  'year',
  'surgeon_yearly_load',
  # 'years_after_initial_certification',
  "had_assist_surg"
  # hospital--
  # 'hospital_icu',
  # 'hospital_urban',
  # 'hospital_beds_gt_350',
  # 'hospital_icu',
  # 'hospital_rn2bed_ratio',
  # 'hospital_mcday2inptday_ratio'
)

```


The 4 types of cohort definitions were described in details on the "explore_cohort_definition.pdf" in the repo.

## 4 cohort definitions

1. using ABS and fellowship council data to exclude fellowship trained surgeons.

dataset name: *abs_fc*

```{r}
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/data/abs_medicare_10_20yr.rdata")

#  rename dataset
abs_fc = abs_medicare_10_20yr

rm(abs_medicare_10_20yr)
```

2. using ABS, fellowship council and medicare specialty code to exclude fellowship trained surgeons.

dataset name: *abs_fc_medicare_splty*

```{r}
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/data/abs_medicare_10_20yr_medicare_splty.rdata")

#  rename dataset
abs_fc_medicare_splty = abs_medicare_10_20yr

rm(abs_medicare_10_20yr)
```

3. Exclude non-GS surgeons by practice patterns by meeting minimal number of types of procedures.

dataset name: *pp*

```{r}
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/data/abs_medicare_10_20yr_21_types_procs.rdata")

#  rename dataset
pp = abs_medicare_10_20yr_n_type

rm(abs_medicare_10_20yr_n_type)
```

4. Exclude non-GS surgeons by abs, fellowship council and practice patterns.

dataset name: *abs_fc_pp*

```{r}
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/data/abs_fc_medicare_10_20yr_5_type.rdata")

abs_fc_pp = abs_fc_medicare_10_20yr_n_type

rm(abs_fc_medicare_10_20yr_n_type)
```


## Compare surgeon cohort definitions

The plot below shows the comparisons of the 4 cohort definition above. *Inner join* indicates the common surgeons that the compared datasets share.

### 2 datasets inner join

```{r}
join_n_plot <- function(dt1, dt2) {
  npi_ls1 = dt1 %>% distinct(npi)
  npi_ls2 = dt2 %>% distinct(npi)
  npi_ls12 = inner_join(npi_ls1, npi_ls2)
  
  dt = data.frame(
    dataset_name = factor(c(deparse(substitute(dt1)), deparse(substitute(dt2)), "inner_join"),
                          levels = c(deparse(substitute(dt1)), deparse(substitute(dt2)), "inner_join")),
    n_suregons = c(nrow(npi_ls1), nrow(npi_ls2), nrow(npi_ls12))
  ) 
  
  p = ggplot(data = dt,
         aes(x = dataset_name, y = n_suregons)) +
    geom_col(width = 0.5) +
    geom_text(aes(label = n_suregons),  vjust = -0.25) +
    scale_y_continuous(limits=c(0, 12000), n.breaks = 2) +
    labs(x = "", y = "") +
    theme_classic()
  
  p
}


(join_n_plot(abs_fc, abs_fc_medicare_splty) |
  join_n_plot(abs_fc, pp) ) /
  (join_n_plot(abs_fc, abs_fc_pp) |
  join_n_plot(abs_fc_medicare_splty, pp)) /
  (join_n_plot(abs_fc_medicare_splty, abs_fc_pp) |
  join_n_plot(pp, abs_fc_pp)) +
  plot_annotation(title = "number of surgeons in each dataset cohort")
  
```


Combine all the *inner join groups* and get a cohort that at least met 2 out of the 4 criteria. The combined group are surgeons who are not fellowship trained based on current ABS or fellowship council database, and identified as general surgery specialty in NPPES or met practice pattern criteria.


```{r}
inner_joined_npi <- function(dt1, dt2) {
  npi_ls1 = dt1 %>% distinct(npi)
  npi_ls2 = dt2 %>% distinct(npi)
  inner_join(npi_ls1, npi_ls2)
}



inner_joined_all_npi = list(inner_joined_npi(abs_fc, abs_fc_medicare_splty),
     inner_joined_npi(abs_fc, pp),
     inner_joined_npi(abs_fc, abs_fc_pp),
     inner_joined_npi(abs_fc_medicare_splty, pp),
     inner_joined_npi(abs_fc_medicare_splty, abs_fc_pp),
     inner_joined_npi(pp, abs_fc_pp)) %>% 
  reduce(full_join) 

```


The number of surgeons in the combined 4 criteria group is `r nrow(inner_joined_all_npi)`.

### 3 groups inner join

```{r}
join_3n_plot<- function(dt1, dt2, dt3) {
  npi_ls1 = dt1 %>% distinct(npi)
  npi_ls2 = dt2 %>% distinct(npi)
  npi_ls3 = dt3 %>% distinct(npi)
  npi_ls123 = list(npi_ls1, npi_ls2, npi_ls3) %>% reduce(inner_join)
  
  
  dt = data.frame(
    dataset_name = factor(
      c(
        deparse(substitute(dt1)),
        deparse(substitute(dt2)),
        deparse(substitute(dt3)),
        "inner_join"
      ),
      levels = c(
        deparse(substitute(dt1)),
        deparse(substitute(dt2)),
        deparse(substitute(dt3)),
        "inner_join"
      )
    ),
    n_suregons = c(nrow(npi_ls1), nrow(npi_ls2), nrow(npi_ls3), nrow(npi_ls123))
  )
  
    p = ggplot(data = dt,
           aes(x = dataset_name, y = n_suregons)) +
      geom_col(width = 0.5) +
      geom_text(aes(label = n_suregons),  vjust = -0.25) +
      scale_y_continuous(limits=c(0, 12000), n.breaks = 2) +
      labs(x = "", y = "") +
      theme_classic()
    
    p
}

join_3n_plot(abs_fc, abs_fc_medicare_splty, pp)  /
join_3n_plot(abs_fc, abs_fc_medicare_splty, abs_fc_pp) /
join_3n_plot(abs_fc, pp, abs_fc_pp) /
join_3n_plot(abs_fc_medicare_splty, pp, abs_fc_pp) +
  plot_annotation(title = "number of surgeons in each dataset cohort")

```


Combine all the *inner join groups* and get a cohort that at least met 3 out of the 4 criteria. The combined group are surgeons who are not fellowship trained based on current ABS or fellowship council database, and identified as general surgery specialty in medicare or met practice pattern criteria.


```{r}
inner_joined_3npi <- function(dt1, dt2, dt3) {
  npi_ls1 = dt1 %>% distinct(npi)
  npi_ls2 = dt2 %>% distinct(npi)
  npi_ls3 = dt3 %>% distinct(npi)
  list(npi_ls1, npi_ls2, npi_ls3) %>% reduce(inner_join)
}



inner_joined_all_3npi = list(inner_joined_3npi(abs_fc, abs_fc_medicare_splty, pp),
                            inner_joined_3npi(abs_fc, abs_fc_medicare_splty, abs_fc_pp),
                            inner_joined_3npi(abs_fc, pp, abs_fc_pp),
                            inner_joined_3npi(abs_fc_medicare_splty, pp, abs_fc_pp)
                            ) %>% 
  reduce(full_join) 


# npi_ls1 = abs_fc %>% distinct(npi)
# npi_ls2 = abs_fc_pp %>% distinct(npi)
# npi_ls3 = abs_fc_medicare_splty %>% distinct(npi)
# npi_ls4 = pp %>% distinct(npi)
# all_4 =  list(npi_ls1, npi_ls2, npi_ls3, npi_ls4) %>% reduce(inner_join)
# 
# full_join(npi_ls3, npi_ls2) %>% nrow()
```


The number of surgeons in the combined 4 criteria group is `r nrow(inner_joined_all_3npi)`.


## Descriptive and model results for the combined dataset above

## At least in 2 datasets

### Table 1

```{r}
combined_4_dataset = abs_fc %>% filter(npi %in% inner_joined_all_npi$npi)

model_dt = prep_model_ready_dt(combined_4_dataset)
```

*case level*

```{r}
# case level 
model_dt %>% 
  select(!!covariates, -year, - surgeon_yearly_load) %>% 
  tbl_summary(by = re_cert_bin) %>% 
  add_p() %>% 
  as_kable_extra()
```

*Surgeon level*

```{r}
# surgeon level
model_dt %>%
  distinct(npi, re_cert_bin, surgeon_yearly_load) %>%
  group_by(re_cert_bin) %>% 
  summarise(n_surgeon = n_distinct(npi),
            yearly_case_mean = mean(surgeon_yearly_load),
            yearly_case_median = median(surgeon_yearly_load)) %>% 
  flextable() %>% 
  autofit()
  
```


### Model

```{r, eval=FALSE}
# run model
f = formula(paste("death_30d ~ 1", paste(covariates, collapse = ' + '),
                  "(1 | procedure)",
                  sep = " + "))

combined_4_death = glmer(formula = f,
                        data = model_dt,
                        family = binomial)

save(combined_4_death, file = "/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_death.rdata")
```


```{r}
# load model
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_death.rdata")
```


#### Death

```{r}
combined_4_death@call$formula
```


*Regression table*

```{r}
tidy(combined_4_death) %>%
  filter(!str_detect(term, "sd")) %>% 
  transmute(term,
            estimate = round(estimate, 3),
            OR = exp(estimate),
            OR = round(OR, 3),
            p_value = round(p.value, 3)) %>% 
  flextable() %>% 
  autofit()
```

#### Severe complication

Since POA flags only become available after 2010, so the patient outcomes from medicare only include 2010-2018.

```{r, eval=FALSE}
# severe cmp 
model_dt_cmp = model_dt %>%
  mutate(severe_complication_no_poa = as.numeric(severe_complication_no_poa)) %>% 
  filter(year>2)

# model_dt_cmp %>% count(year,severe_complication_no_poa)

# run model
f = formula(paste("severe_complication_no_poa ~ 1", paste(covariates, collapse = ' + '),
                  "(1 | procedure)",
                  sep = " + "))

combined_4_cmp = glmer(formula = f,
                        data = model_dt_cmp,
                        family = binomial)

save(combined_4_cmp, file = "/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_cmp.rdata")

```

```{r}
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_cmp.rdata")
```


```{r}
combined_4_cmp@call$formula
```


*Regression table*

```{r}
tidy(combined_4_cmp) %>%
  filter(!str_detect(term, "sd")) %>% 
  transmute(term,
            estimate = round(estimate, 3),
            OR = exp(estimate),
            OR = round(OR, 3),
            p_value = round(p.value, 3)) %>% 
  flextable() %>% 
  autofit()
```




## At least in 3 datasets

### Table 1

```{r}
combined_4_dataset = abs_fc %>% filter(npi %in% inner_joined_all_3npi$npi)

model_dt = prep_model_ready_dt(combined_4_dataset)
```

*case level*

```{r}
# case level 
model_dt %>% 
  select(!!covariates, -year, - surgeon_yearly_load) %>% 
  tbl_summary(by = re_cert_bin) %>% 
  add_p() %>% 
  as_kable_extra()
```

*Surgeon level*

```{r}
# surgeon level
model_dt %>%
  distinct(npi, re_cert_bin, surgeon_yearly_load) %>%
  group_by(re_cert_bin) %>% 
  summarise(n_surgeon = n_distinct(npi),
            yearly_case_mean = mean(surgeon_yearly_load),
            yearly_case_median = median(surgeon_yearly_load)) %>% 
  flextable() %>% 
  autofit()
  
```


### Model

```{r, eval=FALSE}
# run model
f = formula(paste("death_30d ~ 1", paste(covariates, collapse = ' + '),
                  "(1 | procedure)",
                  sep = " + "))

combined_4_death_3dt = glmer(formula = f,
                        data = model_dt,
                        family = binomial)

save(combined_4_death_3dt, file = "/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_death_3dt.rdata")
```


```{r}
# load model
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_death_3dt.rdata")
```


#### Death

```{r}
combined_4_death_3dt@call$formula
```


*Regression table*

```{r}
tidy(combined_4_death_3dt) %>%
  filter(!str_detect(term, "sd")) %>% 
  transmute(term,
            estimate = round(estimate, 3),
            OR = exp(estimate),
            OR = round(OR, 3),
            p_value = round(p.value, 3)) %>% 
  flextable() %>% 
  autofit()
```

#### Severe complication

Since POA flags only become available after 2010, so the patient outcomes from medicare only include 2010-2018.

```{r, eval=FALSE}
# severe cmp 
model_dt_cmp = model_dt %>%
  mutate(severe_complication_no_poa = as.numeric(severe_complication_no_poa)) %>% 
  filter(year>2)

# model_dt_cmp %>% count(year,severe_complication_no_poa)

# run model
f = formula(paste("severe_complication_no_poa ~ 1", paste(covariates, collapse = ' + '),
                  "(1 | procedure)",
                  sep = " + "))

combined_4_cmp_3dt = glmer(formula = f,
                        data = model_dt_cmp,
                        family = binomial)

save(combined_4_cmp_3dt, file = "/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_cmp_3dt.rdata")

```

```{r}
load("/Volumes/George_Surgeon_Projects/MOC_vs_Outcome/model/combined_4_cmp_3dt.rdata")
```


```{r}
combined_4_cmp_3dt@call$formula
```


*Regression table*

```{r}
tidy(combined_4_cmp_3dt) %>%
  filter(!str_detect(term, "sd")) %>% 
  transmute(term,
            estimate = round(estimate, 3),
            OR = exp(estimate),
            OR = round(OR, 3),
            p_value = round(p.value, 3)) %>% 
  flextable() %>% 
  autofit()
```